Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-13 sections/correlated-sicm-and-fm.tex

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
differentiation of stem cells \cite{Gorelik2008}. The SSCM has also been used for correlating 
topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012}. 
Furthermore, it has been utilized in studies investigating endocytotic pathways 
\cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged
clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-coated
pit formation and maturation revealed the effect of mutations in the Dynamin~2
gene on the maturation and internalisation of clathrin coated pits \cite{Ali2019}.

>>>>

SSCM has been used for investigating the dynamics of the interaction of
Cy3-labeled polyoma virus-like particles (VLPs) with Cos-7 cells
(Fig.~\ref{fig:sicm+scm}b,d) \cite{Gorelik2002a}, for the investigation of the
uptake of fluorescent nanoparticles in immortalized human alveolar epithelial
type 1 (AT1) cells and AT2 cells \cite{Kemp2008,Novak2014} and for investigating the
differentiation of stem cells \cite{Gorelik2008}. The SSCM has also been used for correlating 
topography and t-tubule distribution in cardiomyocytes \cite{Lyon2012}. 
Furthermore, it has been utilized in studies investigating endocytotic pathways 
\cite{Shevchuk2008} (Fig.~\ref{fig:sicm+scm}c) and in a study revealing an alternative closing
mechanism for clathrin-coated pits by recording topography simultaneously with
the fluorescence of tagged actin-binding protein and the tagged
clathrin light-chain \cite{Shevchuk2012}. A further study on clathrin-mediated endocytosis revealed the effect of mutations in the Dynamin~2
gene on the maturation and internalisation of clathrin coated pits \cite{Ali2019}.
